On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-22 paper/paper.tex
spelling
Started expansion of related work section

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artifical control flow combinators
  are used instead.

@@

\subsection{Overview}

@@

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.

@@

\subsection{Overview}
\label{sec:Overview}

@@

There is other recent work using deep embeddings in functional languages for 
system development.  One example is the Ivory language \cite{Elliott2015-Ivory} 
which provides a deeply embedded DSL for use in programming high assurance
systems,  However, it's syntax is typical of a deep EDSL and requires additional 
keywords and structures above idiomatic Haskell.

The Feldspar project~\cite{Axelsson:10:Feldspar,Axelsson,Svenningsson:13:Combining}
is a Haskell embedding of a monadic interface
that targets C, and focuses on high-performance. Interestingly, this work
also attempt to make use of both deep and shallow embeddings inside a single
implementation. Both Feldspar and and our work use some form
of monadic reification technology~\cite{Persson:11:MonadicDSL,Svenningsson:13:Compositional,Sculthorpe:13:ConstrainedMonad}.

Svenningsson and Axelsson~\cite{Svenningsson:13:Combining}
explored combining deep and shallow embedding.  They used
a deep embedding as a low level language, then extended
the deep embedding with a shallow embedding written on top
of it. Haskell type classes were used to minimize the effort of adding
new features to the language.

Elliott developed GHC plugins~\cite{github:lambda-ccc}\cite{github:reification-rules}
for compiling Haskell to hardware~\cite{github:Elliott:Talk:2015},
using worker-wrapper style transformations equivalent to the \verb|abs| and
\verb|rep| transformations described in Section \ref{sec:Overview}. These plugins were later generalized to enable additional interpretations~\cite{Elliott:2017}.
